---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cellviz3d

The goal of {cellviz3d} is to propose visualization for segmentized images issued from 3D/4D microscopy. This can be linked with outputs from MorphographX with [{mgx2r}](https://github.com/marionlouveaux/mgx2r) <!--or Mamut with [{mamut2r}](https://github.com/marionlouveaux/mamut2r)-->

## Installation

You can install the released version of {cellviz3d} from [Github](https://github.com/marionlouveaux/cellviz3d) with:

``` r
# install.packages("devtools")
devtools::install_github("marionlouveaux/cellviz3d")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```

## Code of conduct

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.
